\documentclass[12pt, a4paper]{article}
\usepackage[UKenglish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{mathtools} % an extension of amsmath
\usepackage{amsthm, amssymb, amsfonts, amstext}
\usepackage{longtable}
\usepackage{tocloft}
\usepackage{geometry}
\usepackage{algpseudocode}
\usepackage{multicol}
\geometry{margin=27mm}
\usepackage{listings}
\usepackage{xcolor,colortbl}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{makecell}
\renewcommand\theadalign{bc} % to leave lines inside a table
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0,0,0}
\definecolor{pageBG}{rgb}{0,0,0}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{yellow},
    keywordstyle=\color{red},
    numberstyle=\color{red},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize\color{codegreen},
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=4
}
\lstset{style=mystyle}
\urlstyle{same}

\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem*{claim}{Claim}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
% \numberwithin{equation}{section}
\newcommand{\textsb}{\textsubscript}

\title{Algorithms Analysis \& Design\\Project Proposal Viva Questionnaire}
\author{Aditya Harikrish\\2020111009}
\date{}

\begin{document}
\maketitle

\begin{description}
    \item[Q1.] \bfseries What is your driving force for the project/ why have you chosen your respective project? Why are you suitable to do your project?
        \normalfont
    \item[A1.] My project is to make a handbook that would server as a beginner's guide to dynamic programming. It starts with an intuitive introduction to dynamic programming, the need behind it and goes on to present 12 or more problems and their solutions using dynamic programming (along with competing solutions and a comparison of different solutions whenever applicable).

        My primary motivation is that I like to organise information and explain topics that I have learnt in a manner. This is something that I might have done even if I did not have this project as I also like solving challenging problems that keep me busy for days.

    \item[Q2.] \textbf{How should we evaluate you?}
    \item[A2.] I would like to be evaluated on the basis of the ratio of the depth and breadth of the topics covered in the handbook to the ease of understanding the topics for a beginner.

        It is not feasible to cover all aspects of dynamic programming or to explore it to the depth of the work done on dynamic programming by researchers. This is simply to serve as a short and concise handbook that hopes to create the intuition behind dynamic programming.

    \item[Q3.] \textbf{What feedback did you receive during the project proposal viva, if any?}
    \item[A3.] Prof. Kannan said, and I quote, ``Good.''
\end{description}

\end{document}